---
title: "KNN occupancy V2"
format: html
editor: visual
---

## Team

Writer : Jonah Cabayé

Corrector : Bruno Santana

## Business Understanding

---
Accurate occupancy detection of an office room from light, temperature, humidity and CO2 measurements using statistical learning models.
---

## Errors Documentation

---
Row 69 - Missing calling cntDiag to see result
Row 73 - Missing %\>% on relevel function and calling "Occupancy" instead of "No occupancy"
Row 99 - The dataframe CleanDF was not called in summary function
Row 122 - Missing x value on numerator (min-max formula)
Row 186 - Function 'confusionMatrix' not called
---

## Setup packages

```{r}
#install.packages(tidyverse)
#install.packages(class)
#install.packages(caret)
library(tidyverse)
library(class)
library(caret)
```

## Read data

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s1y2223-jonahcby/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
```

## Data Understanding

```{r}
str(rawDF)
```

## Data preparation

```{r}
# Randomizing order of the dataset
cleanDF <- rawDF[sample(1:nrow(rawDF)),]
```

```{r}
#Excluding the column first column because it is not a valuable variable for the model
cleanDF <- cleanDF[-1]
head(cleanDF)
```

## Data understanding: proportion between categories

```{r}
cntDiag <- table(cleanDF$Occupancy)
propCat <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
propCat
```

\## It means there is 6414 unit = 0 and 1729=1 So there is 78.8% of 0 and 21.2 of 1

## Renaming categories

### Error 1 - Missing %\>% on relevel function and calling "Occupancy" instead of "No occupancy"

```{r}
#cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("0","1"), labels = c("No occupancy","Occupancy"))  relevel("Occupancy")
#head(cleanDF, 10)
```

### Correction

```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("0","1"), labels = c("No occupancy","Occupancy")) %>%  relevel("No occupancy")
head(cleanDF, 10)
```

## Data understanding: proportion between categories (after renaming)

```{r}
cntDiag2 <- table(cleanDF$Occupancy)
propCat2 <- round(prop.table(cntDiag2) * 100 , digits = 1)

cntDiag2
propCat2
```

## Analyzing variables

### Error 2 - The dataframe CleanDF was not called

```{r}
#summary(c("Temperature","Humidity","Light","CO2","HumidityRatio","Occupancy"))
```

### Correction

```{r}
summary(cleanDF[c("Temperature","Humidity","Light","CO2","HumidityRatio","Occupancy")])
```

##Replacing missing values

### This step is not necessary since there is no missing values in this dataset

```{r}
#cleanDF[is.na(cleanDF)] <- 0
#summary(cleanDF[c("Temperature","Humidity","Light","CO2","HumidityRatio","Occupancy")])
```

## Normalizing variables

### Error 3 - Missing x value on numerator (min-max formula)

```{r}
#normalize <- function(x) {
#  return (( min(x)) / (max(x) - min(x)))}
```

### Correction

```{r}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))}
```

```{r}
#reoerdering columns to make Occupancy the first column
cleanDF <- cleanDF[, c(6, 1, 2, 3, 4,5)]

head(cleanDF)
```

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(2:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()
```

```{r}
summary(cleanDF_n[,1:5])
```

### Commenting this session because it is not needed for the model

```{r}
#normalize <- function(x) { # Function takes in a vector
#  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
#}

#testSet1 <- c(1:5)
#testSet2 <- c(1:5) * 10

#cat("testSet1:", testSet1, "\n")
#cat("testSet2:", testSet2, "\n")
#cat("Normalized testSet1:", normalize(testSet1), "\n")
#cat("Normalized testSet2:", normalize(testSet2))
```

```{r}
trainDF_feat <- cleanDF_n[1:4071,  ]
testDF_feat <- cleanDF_n[4072:8143,  ]

trainDF_labels <- cleanDF[1:4071,  1]
testDF_labels <- cleanDF[4072:8143,  1]
```

## Modeling

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_test_pred)
```

### Error 4 - Function 'confusionMatrix' not called

```{r}
#(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

## Visualizing tests

```{r}
#install.packages(psych)
library(psych)
pairs.panels(cleanDF_n, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )
```
